\section{Professional Experience}

\cventry
{Security Engineer} % Job title
{adorsys GmbH \& Co. KG} % Organization
{Remote, CM} % Location
{Dec/2023 - Present} % Date
\begin{cvitems}
\item {Technical implementation of client endpoint protection (EPP) solutions.}
\item {Provided DevOps support for EUDI Wallet, ensuring seamless integration and deployment.}
\item {Acted as a Project Maintainer, overseeing the development lifecycle and ensuring project objectives were met.}
\end{cvitems}

\cventry
{Cybersecurity Engineer Intern} % Job title
{Port Authority of Kribi, PAK} % Organization
{Kribi, CM} % Location
{02/2023 - 08/2023} % Date
{
\begin{cvitems}
\item {Designed and implemented a Security Information and Event Management (SIEM) system to enhance threat detection capabilities.}
\item {Performed testing and deployment of computer hardware to optimize network security infrastructure.}
\item {Provided user assistance and support, ensuring smooth operations and addressing security concerns promptly.}
\end{cvitems}
}

\cventry
{Pre-Engineer Network Security Intern} % Job title
{General Delegation for National Security, DGSN} % Organization
{Yaoundé, CM} % Location
{07/2022 - 10/2022} % Date
{
\begin{cvitems}
\item {Designed and implemented a Network Access Control (NAC) system to regulate network access and enhance security posture.}
\item {Conducted asset mapping exercises to identify critical network assets and vulnerabilities.}
\item {Implemented risk management strategies and performed network monitoring to mitigate potential threats.}
\end{cvitems}
}

\cventry
{IT Manager} % Job title
{Association APSF and ACMALEF} % Organization
{Yaoundé, CM} % Location
{08/2022 - present} % Date
{
\begin{cvitems}
\item {Administered the website amouretpartage.ovh, ensuring its smooth operation and security.}
\item {Managed various social media pages, effectively communicating with stakeholders and promoting organizational objectives.}
\end{cvitems}
}